\begin{savequote}[75mm] 
”The world is a country which nobody ever yet knew by description; one must travel through it one's self to be acquainted with it.”
\qauthor{Philip Stanhope, 4th Earl of Chesterfield} 
\end{savequote}

\chapter{Introduction} %1/2 - 1 page
\section{Methodology and Concept}
\subsection{Methodology}
\lettrine[lines=1]{\color{Crimson}D}{eveloping} software is a costly and time consuming process. During the last years, several development methodologies have sprung to address this issue. Examples of such methodologies would be Scrum, Agile and the evolutionary approach. In this particular case an amalgam of practices from the afore-mentioned were chosen to ensure a succesful and less time-consuming development.
\newpage
\subsection{Concept}
\lettrine[lines=1]{\color{Crimson}T}{he} project ended up going through several concepts as more features were added. The initial concept had a game play similar to The NetHack DevTeam's game Nethack\cite{c.nethack}, where the player character had to go through an elaborate labyrinth, fight various creatures and gain experience points to increase statistics[\textcolor{Crimson}{Ch.2}] and items to reach the end of the map. Another idea was to develop a platformer, in the style of the classic Nintendo game, Mario but with various puzzles that the player had to analyze and figure out the best method to complete. As the second idea involved much greater work than the latter one, given, each puzzle had to be manually made, it was given a low priority. A merge between the two was decided upon, where players would be able to fight through the labyrinth of monsters, collect coins and use them to make upgrades and solve various intuitive puzzles. Examples of upgrades were better weapons and armor. Such upgrades would be similar to the concept of levelling, something that many players appreciate. Most earlier presented ideas were kept and in addition to other improvements the enemy creature concept was expanded upon. Having only one enemy type would become very boring, very quickly. Thus, expanding on the concept, the various and diverse enemy types ended up being the major part of the final game.
\afterpage{\clearpage}