\begin{savequote}[75mm] 
”Science is what we have learned about how to keep from fooling ourselves.”
\qauthor{Richard P. Feynman} 
\end{savequote}

\chapter{Thoughts}
\section{Particularities}
\lettrine[lines=1]{\color{Crimson}C}{ertain} things had to be considered for the project. Specifically, a limit on the game world was required so that the project would not get too bloated and end up requiring an impossible amount of time to finish. Thus, a procedural generation system was decided to be put in place. Having a finite number of enemies in the game world was also a requirement to avoid an inhumane amount of time to complete. During development an issue sprung, the issue common to most aspiring game developers: the naive infinite loop resulted in variable framerate and variable time difference that made the game nondeterministic.\cite{Fabien2012} Finally, the engine itself needed to be functional aswell as practical.
\section{Acknowledgments}
\lettrine[lines=1]{\color{Crimson}I}{ would} like to first thank the members of the dissertation committee - not only for their time and patience, but for their intellectual contributions to my development as a scientist. I am indebted to and I would like to thank my thesis advisor, Prof. Cosmin Bonchis. I would like to thank my teachers for their contribution in helping me become better aquainted with Computer Science. Finally, but not least, I would like to thank my colleagues for the fun and support. Thank you for everything that helped me get to this day.
\afterpage{\clearpage}